\documentclass{resume} % Use the custom resume.cls style
 
\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Kochur Viktor} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+7 977 427 97 92 \\ Citizenship: Uzbekistan \\ Current Location: Moscow, Russia} 
\address{\href{mailto:vitekkochur@gmail.com}{vitekkochur@gmail.com} \\ \href{https://www.linkedin.com/in/viktor-kochur-a93132180/}{LinkedIn} \\ \href{https://github.com/Bfalse123}{GitHub}}  %
 
\begin{document}
 
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
 
\begin{rSection}{Education}
 
{\bf MISiS University of Science and Technology}, Moscow, Russia \hfill {Sep 2019 - Jun 2023}\\
Bachelor's in Computer Science\\

{\bf DevOps Summer School HSE} Moscow, Russia \hfill {Aug 2022}\\
Containerization and CI/CD technologies
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\
 
 
\end{rSection}
 
%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Hard Skills & C/C++, Python, C\#, SQL  \\
& Algorithms/data structures, Docker, Git, GitLab CI, TCP/IP \\
& Linux, PostgreSQL, protobuf, Manual Testing, cmake \\ \\
Soft Skills & Time Management, Teamwork, Communication, Stress-resistance\\

Languages & Russian: Native, English: Advanced, French: Elementary\\
\end{tabular}\\
\end{rSection}
 
 
 
%----------------------------------------------------------------------------------------
% Projects
%----------------------------------------------------------------------------------------
\begin{rSection}{PROJECTS}
\vspace{-1.25em}
\item \textbf{Online photo gallery} {(PHP, HTML, MySQL)} \hfill
\begin{itemize}
    \itemsep -3pt {} 
     \item Implemented an authentication system, Collected and stored data in a database.
     \item Implemented simple HTML interface.
 \end{itemize}
 
\item \textbf{Json Parser} {(C++, STL, json)} \hfill
\href{https://github.com/Bfalse123/jsonparser}{GitHub}
 
\item \textbf{Transport Directory} {(C++, STL, protobuf, SVG, cmake)} \hfill \href{https://github.com/Bfalse123/TransportDirectory}{GitHub}
\begin{itemize}
    \itemsep -3pt {} 
     \item Finds the quickest way from one bus station to another.
     \item Draws the whole bus routes map using SVG.
 \end{itemize}

 \item \textbf{Lite Python Interpreter} {(C++, STL, Python, cmake)} \hfill \href{https://github.com/Bfalse123/LitePythonInterpreter/}{GitHub}
\begin{itemize}
    \itemsep -3pt {} 
     \item Analyzes python code.
     \item Compiles this code.
 \end{itemize}
 
 \item \textbf{Mahjong game} {(Unity, C\#, MS SQL)} \hfill
\begin{itemize}
    \itemsep -3pt {} 
     \item Created a game with main menu, leader board and playing field.
     \item Conducted manual testing of the game.
 \end{itemize}
\end{rSection} 
 
 
%----------------------------------------------------------------------------------------
\begin{rSection}{EXPERIENCE}
 
\textbf{C\#/Unity Developer, HerbariumGames} \hfill Feb 2020 - July 2020 (6 months)\\
Implemented mini-games and worked with interface. I learned teamwork and working with Git.
 
\end{rSection} 
 
 
\begin{rSection}{Extra-Curricular Activities} 
\begin{itemize}
    \item Development in C++ (5 coursers) \hfill
    Yandex \& E-Learning Development Fund, Moscow Institute of Physics and Technology \hfill \href{https://drive.google.com/file/d/1d1d4hC7YXxu3HGqzQ9vJUY29GPHpFAra/view?usp=sharing}{Certificate} 
    \item Algorithms/data structures Training \hfill Yandex
    \item "14 Days Study Plan to Crack Algo" \hfill Leetcode
    \item Database: Basics and Theory \hfill VK Team
\end{itemize}
 
 
\end{rSection}
 
%------------------------
% Use this more detailed section if you have Relevant work experience
% keep your resume to 1 page, if you need to remove a project to display relevant experience
% that is okay
% ----------------------------
 
 
%----------------------------------------------------------------------------------------
 
 
 
\end{document}
